My title

### 2024-04-04 paper/paper.qmd
updates to data and data cleaning

library(tidyverse)
library(tinytex)
library(knitr)
library(janitor)
library(kableExtra)
library(ggplot2)

@@

The remainder of this paper is structured as follows. @sec-data....

@@

```{r}
#| label: fig-rawdataNKE
#| fig-cap: Description of Raw Nike Stock Columns and How They Were Cleaned
#| echo: false

@@

cleaned_data_NKE |>
  ggplot(mapping = aes(x = Date, y = Close)) +
  geom_line(color="grey") +
  theme_light() +
  labs(x = "July 11th, 1991 to May 19th, 1998", y = "Stock Price at Closing")

@@

# Appendix {-}

>>>>

library(tidyverse)
library(tinytex)
library(kableExtra)
library(knitr)
library(janitor)
library(kableExtra)
library(ggplot2)

@@

In [Background], the history of why each company was or is being boycotted is explained. In the following section, [Data],

# Background

## Nike (NKE)

In August of 1992, Jeffrey Ballinger published “The new free-trade heel: Nike's profits jump on the backs of Asian workers” in a Harper’s Magazine issue [@harpers]. This publication revealed the low pay and poor working conditions in Nike’s Indonesian sweatshops. Later that year, Nike released the “Code of Conduct and Memorandum of Understanding” for contract workers, but the labour controversy was well underway. In the following years, protests in Southeast Asia and the United States raged on. Protests at the Barcelona Olympics in 1992 and the founding of Ballinger’s labour group Press for Change in 1993 brought new waves of media attention to the cause.

## United Parks and Recreation

## Chevron

## Starbucks

@@

In @tbl-rawdataNKE, the data's date and stock price are shown.

```{r}
#| label: tbl-rawdataNKE
#| tbl-cap: "Description of Raw Nike Stock Variables"
#| echo: false

rawdataNKE <- data.frame( 
  "Variables" = c( "Date", "Close"),
  "New Name" = c( "Date", "Stock Price"), 
  "Description of Variables" = c("The day of the stock price", "The value of the stock at market close"), 
  "Example Value" = c("1991-07-12", "1.355469")
)

knitr::kable(rawdataNKE, 
      col.names = c("Variables", 
                    "New Name",
                    "Description of Variables" ,
                    "Example Value"),
      booktabs = TRUE,
      linesep = " "
      )
```

@@

cleaned_data_NKE |>
  ggplot(mapping = aes(x = Date, y = Close)) +
  geom_line(color="pink") +
  labs(x = "July 11th, 1991 to May 19th, 1998", y = "Stock Price at Closing",) +
  scale_x_date(
    breaks = "12 months",
    labels = scales::label_date_short(
      format = c("%y", "%b"),
      sep = "\n"))
  ylim(1,2) + 
  theme_minimal()

@@

# Appendix {.unnumbered}
